%----------------------------------------------------------------------
% Top-level declarations for the cover letter for a set of status and
% participant site check mailers.
%----------------------------------------------------------------------
\documentclass[letterpaper,12pt]{letter}

%----------------------------------------------------------------------
% Common definitions.
%----------------------------------------------------------------------
\include{d:/cdr/mailers/include/template}

%----------------------------------------------------------------------
% Package and macro used for special symbols, such as \texteuro.
%----------------------------------------------------------------------
\usepackage{textcomp}
\newcommand{\Special}[1]{{\fontencoding{T1}\selectfont\symbol{#1}}}

\usepackage{graphicx}

%----------------------------------------------------------------------
% Eliminate warnings on overfull hbox by adjusting the stretch parameters
%----------------------------------------------------------------------
\tolerance=1000
\emergencystretch=20pt

%----------------------------------------------------------------------
% Package and code to set double-quotes correctly.
%----------------------------------------------------------------------
\usepackage{ifthen}
\newcounter{qC}
\newcommand{\tQ}{%
    \addtocounter{qC}{1}%
    \ifthenelse{\isodd{\value{qC}}}{``}{''}%
}

%----------------------------------------------------------------------
% Set up the margins.
%----------------------------------------------------------------------
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{0in}
\setlength{\parskip}{12pt}
\setlength{\parindent}{0mm}
\setlength{\headheight}{-.5in}

%----------------------------------------------------------------------
% Start the document and import the standard mailer templates.
%----------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------
% Don't put a page number on this page.
%----------------------------------------------------------------------
\thispagestyle{empty}

%----------------------------------------------------------------------
% Lay out the letterhead.
%----------------------------------------------------------------------
\LetterheadWithLogo
  
\vspace{20pt}

\today

@@ADDRESS@@

%----------------------------------------------------------------------
% Suppressed to allow for longer addresses without spilling over
% onto a second page.
%%%\vspace{12pt}
%----------------------------------------------------------------------

Subject: Listing in the NCI's PDQ/Cancer.gov database

\raggedright
The National Cancer Institute's PDQ/Cancer.gov comprehensive database of
cancer information includes a registry of cancer clinical trials being
conducted in the United States and worldwide.  This information is
available on the NCI's Cancer.gov Web site (http://cancer.gov). 
Recently, you were identified as an investigator associated with a
clinical trial that is listed in PDQ/Cancer.gov.  Therefore, your name
and contact information have been listed on the Web site in association
with a participating location for this clinical trial.

Please review the attached listing of information from our database and
indicate any changes or additions needed.  At this time, we would also
like to invite you to have your information published in the
PDQ/Cancer.gov Directory of Physicians who provide cancer treatment. 
Currently, this Directory is not published on the Web, but it may be
made available the future.  Please indicate if you would like to have
your information published in the Directory by checking the appropriate
box on the attached form.  If you do wish to be included, please fill in
the rest of the requested information.  We will then contact you
annually to verify and update this information.

We appreciate your time and effort in helping to keep PDQ/Cancer.gov
current and accurate, and we look forward to receiving your response. 
Should you have any questions, please contact the PDQ/Cancer.gov
Directory Coordinator at 301-402-6722.

\vspace{12pt}

PDQ/Cancer.gov Directory Coordinator \\
Cancer Information Products and Systems

\vfill
\end{document}
