%----------------------------------------------------------------------
% Top-level declarations for the cover letter for a set of status and
% participant site check mailers.
%----------------------------------------------------------------------
\documentclass[letterpaper,12pt]{letter}

%----------------------------------------------------------------------
% Common definitions.
%----------------------------------------------------------------------
\include{d:/cdr/mailers/include/template}

%----------------------------------------------------------------------
% Package and macro used for special symbols, such as \texteuro.
%----------------------------------------------------------------------
\usepackage{textcomp}
\newcommand{\Special}[1]{{\fontencoding{T1}\selectfont\symbol{#1}}}

\usepackage{graphicx}

%----------------------------------------------------------------------
% Package used for special symbols, such as \texteuro.
%----------------------------------------------------------------------
\usepackage{calc}

%----------------------------------------------------------------------
% Eliminate warnings on overfull hbox by adjusting the stretch parameters
%----------------------------------------------------------------------
\tolerance=1000
\emergencystretch=20pt

%----------------------------------------------------------------------
% Package and code to set double-quotes correctly.
%----------------------------------------------------------------------
\usepackage{ifthen}
\newcounter{qC}
\newcommand{\tQ}{%
    \addtocounter{qC}{1}%
    \ifthenelse{\isodd{\value{qC}}}{``}{''}%
}

%----------------------------------------------------------------------
% Set up the margins.
%----------------------------------------------------------------------
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\parskip}{12pt}
\setlength{\parindent}{0mm}
\setlength{\headheight}{-.5in}

%----------------------------------------------------------------------
% Start the document and import the standard mailer templates.
%----------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------
% Don't put a page number on this page.
%----------------------------------------------------------------------
\thispagestyle{empty}

%----------------------------------------------------------------------
% Lay out the letterhead.
%----------------------------------------------------------------------
\LetterheadWithLogo
  
\vspace{36pt}

\today

@@ADDRESS@@

\vspace{12pt}

Subject: Review of PDQ/Cancer.gov protocol abstract

We have not yet received your review of the protocol:

@@PROTOCOLID@@, \\
@@PROTOCOLTITLE@@

Please review the printout and make any changes to the abstract directly on
the printout.  Please pay particular attention to the disease retrieval terms,
which are the cancer types, stages, or conditions used to describe the
trial.  These terms are used for accurate retrieval of this trial on the
Cancer.gov Web site.

Please note that the title may have been modified on Cancer.gov to adhere to a
standard PDQ/Cancer.gov protocol title format.  This format usually includes
the phase of study; drugs, agents or modalities under study; and eligible
diseases or conditions.  Descriptions of endpoints and objectives are
generally not included in the PDQ/Cancer.gov title.  If you have any concerns
about using our format for your PDQ/Cancer.gov abstract, please alert us 
to these concerns when you return the abstract printout.

If significant changes are made in the scientific design of the study, then we
need to receive an IRB approved protocol amendment or a copy of the revised
protocol so that we may incorporate the information accurately into the
protocol abstract.  If a study was originally reviewed by the PDQ/Cancer.gov
Editorial Board prior to listing, the amendment may be re-reviewed prior to
incorporation into PDQ/Cancer.gov.

If the information in the abstract is accurate and no changes are needed,
please initial as indicated on the last page of the attached abstract.  Return
the entire abstract printout in the enclosed self-addressed envelope, or fax
back the initialed form and any changes made to the abstract.  It is important
that your review be returned as soon as possible.  We will ask you to review
the protocol abstract annually as long as the protocol is active.

Health professionals from around the world use the PDQ/Cancer.gov clinical
trials database, available on the NCI's Cancer.gov Web site
(http://cancer.gov), to identify and refer patients to clinical trials for
which they may be eligible.  PDQ/Cancer.gov information is
also available through the NCI's Cancer Information Service (1-800-4-CANCER)
and several online services.

If you have already returned your review of the above protocol, please
disregard this letter.  If your schedule does not permit you to complete this
review within 10 days of receipt of this letter, or if you have any questions,
please feel free to contact the PDQ/Cancer.gov Protocol
Coordinator at ***REMOVED*** (phone), 301-402-6728 (fax), or send email to 
pdqprot@cips.nci.nih.gov.

We appreciate the time and effort involved in helping us to keep the clinical
trials information in PDQ/Cancer.gov current and accurate.

\vspace{12pt}

PDQ/Cancer.gov Protocol Coordinator \\
Cancer Information Products and Systems

\vfill
\end{document}
